Missing Data

### 2021-07-02 analysis/missing.Rmd
refactor: use ameld::plot_dots

.dotplot <- function(x, xlim = c(0, length(x)),
                     col = palette.colors(2L)[2L], pch = 19L) {
    old.par <- par(no.readonly = TRUE)
    on.exit(par(old.par))

    n <- length(x)

    mai <- par("mai")
    w <- max(strwidth(names(x), "inch"), na.rm = TRUE) + 1/16
    if (mai[2L] < w)
        mai[2L] <- mai[4L] + w # taken from dotchart
    par(mai = mai)

    plot(NA, xlim = xlim, ylim = c(0L, n + 1L), axes = FALSE)
    title(main = "Missing Data", adj = 0L)
    title(xlab = "Frequency", adj = 1L)
    y <- seq_len(n)
    mtext(
        names(x), at = y, adj = 0L, side = 2L, las = 2L,
        line = (w + 0.1) / par("csi"), cex = 0.8
    )
    abline(h = y, col = "#808080", lty = "dotted", lwd = 1L)
    points(x, y, col = col, pch = pch)
    axis(1L, lwd.ticks = 0L, col = "#808080")
}

@@

.dotplot(sort(na), xlim = c(0L, nrow(m)))
```

>>>>

@@

plot_dots(sort(na), xlim = c(0L, nrow(m)), main = "Missing Data")
```
